Trauma treatment delay

### 2023-12-14 manuscriptlongversion.Rmd

Rstudio was used to perform the logistical regression. The code was
written to clean and prepare the data from the database. The data was
processed to have the variables customized to fit into the logistical
regression model, such as making them into factors, renaming outcomes in
the database and replacing or removing unknown values. The variables
were either binary or continuous. This code was used on scrambled data
at first so to avoid selection bias as much as possible. When the code
was finished, it was run on the unscrambled data.

@@

The logistical regression is run through Rstudio using the glm command.
It was ran several times to make an ajusted table and 7 unadjusted, one
for each variable. To make the tables, the package gtsummary was used to
visualize the adjusted and unadjusted regression individually, then
merging them together into one table.

@@

Not many studies regarding trauma and patient level factors have had
delayed treatment as their outcome, with many analysing mortality. Some
likeness exist with which patient level factors predict the outcome,
with higher mortality being seen in patients with lower GCS and higher
ISS [@Mort_sam][@Mort_hef]. Increased age was also a factor linked to
mortality, which was not seen to be linked to delayed treatment in this
study. This

When looking at the patient demographic, it is clear that the majority
admitted to trauma care are men, with it being slightly higher in the
delay to treatment group. However, not high enough to be statistically
significant. The fact that gender did not show an increased odds ratio
should be seen as a positive sign. It suggests that among trauma
patients, there is no systematic delay based on this patient level
factor. The same goes for age, as

>>>>

Rstudio was used to clean and prepare the data from the database. The
data was processed to have the variables customized to fit into the
logistical regression model, such as making them into factors, renaming
outcomes in the database and replacing or removing unknown values. The
variables were either binary or continuous. While writing the code, it
was tested on scrambled data so to avoid selection bias as much as
possible. When the code was finished, it was run on the unscrambled data
for a result.

@@

The logistical regression is run through Rstudio using the glm command.
It was ran several times to make an adjusted table and 7 unadjusted, one
for each variable. To make the tables, the package gtsummary was used to
visualize the adjusted and unadjusted regression individually, then
merging them together into one table.

@@

Not many studies regarding trauma and patient level factors have had
delayed treatment as their outcome, with many analysing mortality. Some
likeness exist with which patient level factors predict the outcome,
with higher mortality being seen in patients with lower GCS and higher
ISS [@Mort_sam][@Mort_hef]. Increased age was also a factor linked to
mortality, which was not seen to be linked to delayed treatment in this
study. An older patient is more likely to have co-morbidities that might
affect their mortality but not increase their likelihood of receiving
delayed treatment the same way ISS and GCS does[@Gioffre2018].

When looking at the patient demographic, it is clear that the majority
admitted to trauma care are men, with it being slightly higher in the
delay to treatment group. However, not high enough to be statistically
significant. The fact that gender did not show an increased odds ratio
should be seen as a positive sign. It suggests that among trauma
patients, there is no systematic delay based on this patient level
factor.
